Carbonate chemistry at Ny-Ålesund

### 2022-08-10 awipev-CO2.Rmd
still on finalizing a figure

# Same plot for paper
at_s <- d_all_at_discrete %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
  Mytheme(size_labs = 9)
ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")

@@

```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
# PLOT
print(p_at_s)
rm(p_at_s)
```

@@

# for paper
pco2_calc_meas <- d_all %>% 
  dplyr::select(pco2_fb_insi_temp, pco2_calc_fb_insi_temp) %>% 
  drop_na() %>% 
  ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
  geom_point(col="blue", size = 0.5) +
  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(aes(label = after_stat(eq.label))) +
#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
  theme_bw() + Mytheme(size_labs = 9)
ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
```

@@

offset_ph <- ph_sf %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(aes(x=datetime, y=diff_spec_sf, color="blue"), size=2) +
  geom_hline(yintercept=0, size=0.3) +
  geom_hline(yintercept=-0.02, size=0.3, linetype = "dashed") +
  geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  Mytheme(size_labs = 12, face_font = "plain") + 
  #theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_colour_discrete(guide="none")
ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 10, height = 10, units = "cm")
```
Offset between calibrated seaFET data and pH spectro. The offset must be between -0.2 and 0.2 pH units. "differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al. 2017).

@@

### **Spectro vs seafet**
```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
reg <- ggreg(
  xdata = d_all$ph_s_sf_temp_insi,
  ydata = d_all$pHint_tot_sf,
  type = "MA",
  plot = TRUE,
  title = "pH spec. vs pH seafet (at in situ temperature)",
  xlab = "Spectrophotometric pH",
  ylab = "SeaFET pH",
  proplot = TRUE
)
pHspec_pHcalc <- reg$plot + xlim(c(8.05, 8.20)) + ylim(c(8.05, 8.20))
p
#print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s / pco2_calc_meas / offset_ph / pHspec_pHcalc)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
g
```

>>>>

# # Same plot for paper
# at_s <- d_all_at_discrete %>% 
#   drop_na() %>% 
#   ggplot(aes(x = sal_fb_mix, y = at)) +
#   geom_point(col="blue", size = 0.5) +
#   labs(x="Salinity", y=latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
#   stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
#   Mytheme(size_labs = 9)
# ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")

# for paper
at_s <- d_all_at_discrete %>% 
  dplyr::select(sal_fb_mix, at) %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x= latex2exp::TeX("Salinity"),
       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
  coord_fixed()
at_s
ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")

@@

```{r plot Discrete salinity vs TA, eval, FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
# PLOT
print(p_at_s)
rm(p_at_s)
```

@@

# for paper
pco2_calc_meas <- d_all %>% 
  dplyr::select(pco2_fb_insi_temp, pco2_calc_fb_insi_temp) %>% 
  drop_na() %>% 
  ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
  geom_point(col="blue", size = 0.5) +
  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) + geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
```

@@

offset_ph <- ph_sf %>% 
  drop_na() %>% 
  ggplot() +
  geom_point(aes(x=datetime, y=diff_spec_sf, color="blue"), size=2) +
  geom_hline(yintercept=0, size=0.3) +
  geom_hline(yintercept=-0.02, size=0.3, linetype = "dashed") +
  geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  Mytheme(size_labs = 9, face_font = "plain")+ theme(aspect.ratio=1)  + 
  scale_colour_discrete(guide="none") + 
  coord_fixed()
ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 25, units = "cm")
```
Offset between calibrated seaFET data and pH spectro. The offset must be between -0.2 and 0.2 pH units. "differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al. 2017).

@@

### **Spectro vs seafet**
```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
reg <- ggreg(
  xdata = d_all$ph_s_sf_temp_insi,
  ydata = d_all$pHint_tot_sf,
  type = "MA",
  plot = TRUE,
  title = "pH spec. vs pH seafet (at in situ temperature)",
  xlab = "Spectrophotometric pH",
  ylab = "SeaFET pH",
  proplot = TRUE
)
pHspec_pHcalc <- reg$plot + xlim(c(8.05, 8.20)) + ylim(c(8.05, 8.20))
p
#print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)

pHspec_pHcalc <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")
```

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHcalc)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
g
```
